An Open Platform for Managing Short Programming Exercises

### 2013-06-24 paper/paper.tex
handle whitespace in et. al.
removed ITS from related work

In the Winter 2013 term at Knox College, students taking CS1 used {\tt CloudCoder}.
We collected over 6,000 submissions
for 32 exercises by 23 students. [TODO: what else?]

@@

Denny et. al. have studied novice syntax errors\cite{Denny:2012:SEE:2325296.2325318}
using data collected from the CodeWrite system.
CodeWrite is similar to CloudCoder, except that students create
exercises and test cases for each other to solve, and are evaluated on
the quality of their practice exercises.

Lane et. al. describe Intention-Based Scoring (IBS)\cite{Lane:2005:ISA:1047344.1047471},
an approach to building an ITS for programming whereby human
judges to score or code {\em charettes}, or assignments students work on in a
timed, closed-lab environment.  IBS derives from prior work on
identifying ``bugs'' in online protocols, and as such attempts to
identify places where students have a ``bug'' in their development
process.  This approach, while labor-intensive, shows some promise in
developing an ITS for programming assignments.

Zingaro et. al. built the Python Classroom Response
System\cite{Zingaro:2013:FCP:2445196.2445369}, a system similar to
CloudCoder, except that it focuses on supporting in-class programming
questions for a class that uses a {\em Peer Instruction} pedagogical approach.

Pritchard et. al. present CS Circles\cite{Pritchard:2013:CCI:2445196.2445370},
an interactive on-line
Python curriculum that embeds short questions, some of which involve
programming, directly into the text.  This sort of interactive text
shows great promise for developing open, interactive courses.

@@

%On the other hand, Jin et. al. \cite{Jin:2012:PRA:2345840.2345889, jin-kdd2011} perform

>>>>

In the Winter 2013 term at Knox College, students taking CS1 used {\tt CloudCoder}.
We collected over 6,000 submissions
for 32 exercises by 23 students.

@@

Denny et.\ al. have studied novice syntax errors\cite{Denny:2012:SEE:2325296.2325318}
using data collected from the CodeWrite system.
CodeWrite is similar to CloudCoder, except that students create
exercises and test cases for each other to solve, and are evaluated on
the quality of their practice exercises.

%Lane et.\ al. describe Intention-Based Scoring (IBS)\cite{Lane:2005:ISA:1047344.1047471},
%an approach to building an ITS for programming whereby human
%judges to score or code {\em charettes}, or assignments students work on in a
%timed, closed-lab environment.  IBS derives from prior work on
%identifying ``bugs'' in online protocols, and as such attempts to
%identify places where students have a ``bug'' in their development
%process.  This approach, while labor-intensive, shows some promise in
%developing an ITS for programming assignments.

Zingaro et.\ al. built the Python Classroom Response
System\cite{Zingaro:2013:FCP:2445196.2445369}, a system similar to
CloudCoder, except that it focuses on supporting in-class programming
questions for a class that uses a {\em Peer Instruction} pedagogical approach.

Pritchard et.\ al. present CS Circles\cite{Pritchard:2013:CCI:2445196.2445370},
an interactive on-line
Python curriculum that embeds short questions, some of which involve
programming, directly into the text.  This sort of interactive text
shows great promise for developing open, interactive courses.

@@

%On the other hand, Jin et.\ al. \cite{Jin:2012:PRA:2345840.2345889, jin-kdd2011} perform
